Online {\IterComp}

### 2017-09-13 motivation.tex
motivation done

@@

@@

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-online.pdf}
    \caption{Comparison between the offline and online {\itercomp}.
             The vertical lines represent the average speedups over
             all the 1,000 inputs.}
    \label{fig:motivation-online}
\end{figure}

@@

However, because of the restriction of having a single execution per input,
it is not possible to measure speedup in a real-world online scenario.
Moreover, measuring just execution time, for example, is also not viable since
different inputs often mean different amounts of work,
rendering it meaningless to compare optimizations only by execution time.
Therefore, we need a performance metric which can be profiled from a single
execution of the program.
Although a previous work has suggested that \textit{instructions per cycle}~(IPC)
could be used with that goal, IPC have no correlation with speedup~\citep{fursin07}.
In a case where we have two distinct versions of the program, due to different
optimizations, which is also executed with distinct inputs, higher IPC does not
necessarily mean lower execution time (higher performance).

\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-metric.pdf}
    \caption{Comparison among different performance metrics for performing
             online {\itercomp}.
             The vertical lines represent the best score for each metric.}
    \label{fig:motivation-metric}
\end{figure}

Figure~\ref{fig:motivation-metric} shows a comparison between execution time and IPC,
and their correlation with the actual speedup.
Each point in the figure corresponds to each metric averaged over
a set of inputs, collected during the {\itercomp}.
The vertical lines correspond to the optimization sequence
with the best score for each one of the metrics.
This figure shows that both execution time and IPC are unsuitable for
online {\itercomp}, as they present no direct correlation with the actual
speedup obtained by the optimization sequence being evaluated.

In the remaining of this paper, we develop a work efficiency metric, suitable
for guiding online {\itercomp}, which can be profiled with a single execution
of the program with the optimization sequence being evaluated.

>>>>

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-online.pdf}
    \caption{Histograms of speedup over \texttt{-O3} for each of the 1,000 inputs of XXX. The green histogram shows the speedup when using
    the optimization sequence selected by offline \itercomp, the blue one is the speedup using the optimization sequence selected by an
    online-like approach.}
    \label{fig:motivation-online}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-metric.pdf}
    \caption{Relationship between IPC and execution time vs optimization speedup for XXX different binaries of XXX. Each point represents
	averages over all inputs.}
    \label{fig:motivation-metric}
\end{figure}

This is not an entirely surprising result. Evaluating our optimization decisions on more inputs decreases the chances of optimizing for an
unrepresentative input. Despite that offline \itercomp is still the preferred way. Measuring the speedup caused by an optimization requires
running the same input \textit{at least twice}, one of the optimized and one for the baseline binary. This is either infeasible or
undesirable in a realistic online \itercomp scenario. There are two existing workarounds to this problem: directly comparing the
\textit{execution time} of each run against previous runs or directly comparing the \textit{instructions per cycle}~(IPC)~\citep{fursin07}.
Neither metric is a good proxy for speedup. Figure~\ref{fig:motivation-metric} plots the measured IPC and execution time versus the real
speedup for XXX different binaries of the XXX benchmark. IPC, execution time, and speedup are averaged over all inputs. Both metrics
correlate little with speedup. Different inputs require a different amount of work which dominates the changes in execution time. IPC on
the other hand might improve with a more efficient binary but the opposite can also be true. For example, inserting \texttt{NOP} statements
will usually improve IPC.

In the remaining of this paper, we examine our work efficiency metric, a novel way for approximating optimization speedup through a single
run which can be used to drive an online \itercomp methodology.

@@

% \begin{figure}[t!]
%     \centering
%     \includegraphics[width=0.5\textwidth]{figs/motivation-online.pdf}
%     \caption{Comparison between the offline and online {\itercomp}.
%              The vertical lines represent the average speedups over
%              all the 1,000 inputs.}
%     \label{fig:motivation-online}
% \end{figure}

@@

% However, because of the restriction of having a single execution per input,
% it is not possible to measure speedup in a real-world online scenario.
% Moreover, measuring just execution time, for example, is also not viable since
% different inputs often mean different amounts of work,
% rendering it meaningless to compare optimizations only by execution time.
% Therefore, we need a performance metric which can be profiled from a single
% execution of the program.
% Although a previous work has suggested that \textit{instructions per cycle}~(IPC)
% could be used with that goal, IPC have no correlation with speedup~\citep{fursin07}.
% In a case where we have two distinct versions of the program, due to different
% optimizations, which is also executed with distinct inputs, higher IPC does not
% necessarily mean lower execution time (higher performance).
%
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=0.5\textwidth]{figs/motivation-metric.pdf}
%     \caption{Comparison among different performance metrics for performing
%              online {\itercomp}.
%              The vertical lines represent the best score for each metric.}
%     \label{fig:motivation-metric}
% \end{figure}
%
% Figure~\ref{fig:motivation-metric} shows a comparison between execution time and IPC,
% and their correlation with the actual speedup.
% Each point in the figure corresponds to each metric averaged over
% a set of inputs, collected during the {\itercomp}.
% The vertical lines correspond to the optimization sequence
% with the best score for each one of the metrics.
% This figure shows that both execution time and IPC are unsuitable for
% online {\itercomp}, as they present no direct correlation with the actual
% speedup obtained by the optimization sequence being evaluated.
% 
% In the remaining of this paper, we develop a work efficiency metric, suitable
% for guiding online {\itercomp}, which can be profiled with a single execution
% of the program with the optimization sequence being evaluated.
